How to compute the fusion product of MV cycles in type A

### 2021-04-21 draft.tex
minor mtg edits plus typos from last upload

The variety $X(\tau)$ defined by
% from $\tau\in YT(\lambda)_\mu$ by 
\[
X(\tau) = \overline{
    \{
        A \in  \overline{\OO}^\lambda\cap\TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}
}    
\]
is called a generalized orbital variety.

@@

\begin{proof}
    Let $(A,s)$ be an element of the set on the left hand side, let $a\in\{0,s\}$ and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
    % Let $i\in \{1,\dots,N\}$ and write $m(i)$ for the maximum weight of a box in $\tau'(i)$ or $\tau''(i)$.

    The the Jordan type of $A-a\big|_{E_a\cap\CC^{|\mu(i)|}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
    Moreover, the lattice $(L,s)$ defined by $g(A)$ is such that $t-a$ has the same Jordan type on 
    % $\cO_a^{m(i)} / L(a)\cap\cO_a^{m(i)} = \CC[t]^{m(i)}/L\cap\CC[t]^{m(i)}\otimes_{\CC[t]}\cO_a $ 
    \begin{equation}
        \label{eq:bcflat}
        \cO_a^{|\mu(i)|} / L(a)\cap\cO_a^{|\mu(i)|} = \CC[t]^{|\mu(i)|}/L\cap\CC[t]^{|\mu(i)|}\otimes_{\CC[t]}\cO_a 
    \end{equation}
    as does $(A-a\big|_{E_a\cap\CC^{|\mu(i)|}},s)$. 
    \acom{Not sure when to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
    % 
    % \Cref{eq:bcflat} follows from e.g.\ \cite[Proposition~10.14]{atiyah2018introduction}:
    % \begin{quotation}
    %     If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
    % \end{quotation}
    % applied to $A = \CC[t]$ and $\fa = (t)$. 
    \Cref{eq:bcflat} follows from the fact that a module over a PID is flat if and only if it is torsion free, and $\cO_a$ is clearly torsion free.

@@

\begin{question}
%[Related question] 
    If $\mu',\mu''$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
    \[
    \begin{tikzcd}
        \overline\Gr^{\lambda',\lambda'}_{0,s}\cap S^{\mu',\mu''}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda'} \cap S^{\mu'} \times \overline\Gr^{\lambda'} \cap S^{\mu''} \supset Z' \times Z'' \ar[d]\\
        \overline\OO^{\lambda',\lambda''}_{0,s} \cap \UU^{\mu',\mu''}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda'}\cap \TT_{\mu'}\cap \n \times \overline\OO^{\lambda''}\cap \TT_{\mu''}\cap \n
    \end{tikzcd}    
    \]
\end{question}
% 
\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z',Z''$  be MV cycles of coweight $(\lambda',\mu'),(\lambda'',\mu'')$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
    Then 
    \begin{equation}
        \label{eq:tabmult}
        % Z_\tau\ast Z_\sigma 
        m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
        = 
        % \sum_{Z\in\cZ(\lambda)_\mu} 
        \sum_{\tau\in S(\lambda)_\mu}
        i\left(
            Z(\tau), Z'\circ Z''
            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
        \right) [Z(\tau)]
    \end{equation}
    and the intersection multiplicities on the right are found by\dots\acom{To be completed.}

@@

    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
    $$
    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
        Z, Z' \circ Z''
        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
    \right) b_Z 
    $$
    can also be deduced from \Cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$. These are described in \Cref{lem:mintab,prop:minwts} below.
\end{proposition}
% 
\begin{conjecture}
    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
    % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
    Then 
    \begin{equation}
        i(\tau, 
        % \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}
        % Z_1 \circ Z_2 
        \tau' \circ \tau''
        ) = 1 \,. 
    \end{equation}
\end{conjecture}
%

@@

We view MV cycles as semi-standard young tableaux. Suppose we have two tableaux $\tau'$ and $\tau''$, with respective weights $\lambda'$, $\mu'$ and $\lambda''$, $\mu''$, and we wished to take their fusion product. We consider a generic matrix $X \in \UU^{\mu',\mu''}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda',\lambda''}_{0,s}$.

>>>>

The variety $X(\tau)$ defined by
% from $\tau\in YT(\lambda)_\mu$ by 
\[
X(\tau) = \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}
}    
\]
is called a generalized orbital variety.

@@

\begin{proof}
    Let $A$ be an element of the set on the left hand side, let $a\in\{0,s\}$ and denote by $E_a$ the generalized $a$-eigenspace of $A$. 
    % Let $i\in \{1,\dots,N\}$ and write $m(i)$ for the maximum weight of a box in $\tau'(i)$ or $\tau''(i)$.

    The the Jordan type of $(A-a)\big|_{E_a\cap\CC^{|\mu(i)|}}$ is given by $\lambda'(i)$ if $a = 0$ and $\lambda''(i)$ if $a = s$. 
    Moreover, the lattice $L$ defined by $g(A)$ is such that $t-a$ has the same Jordan type on 
    % $\cO_a^{m(i)} / L(a)\cap\cO_a^{m(i)} = \CC[t]^{m(i)}/L\cap\CC[t]^{m(i)}\otimes_{\CC[t]}\cO_a $ 
    \begin{equation}
        \label{eq:bcflat}
        \cO_a^{|\mu(i)|} / L(a)\cap\cO_a^{|\mu(i)|} = \left(\CC[t]^{|\mu(i)|}/L\cap\CC[t]^{|\mu(i)|}\right)\otimes_{\CC[t]}\cO_a 
    \end{equation}
    as does $(A-a)\big|_{E_a\cap\CC^{|\mu(i)|}}$. 
    % \acom{Not sure when to use $(?,s)$ notation and when not in this proof. Here I just didn't want to end the sentence with the bulky subscript.}
    % 
    % \Cref{eq:bcflat} follows from e.g.\ \cite[Proposition~10.14]{atiyah2018introduction}:
    % \begin{quotation}
    %     If $A$ is a Noetherian ring, $\fa$ an ideal, $\hat A$ the $\fa$-adic completion of $A$, then $\hat A$ is a flat $A$-algebra.
    % \end{quotation}
    % applied to $A = \CC[t]$ and $\fa = (t)$. 
    \Cref{eq:bcflat} follows from the fact that a module over a PID is flat if and only if it is torsion free, and $\cO_a$ is clearly torsion free.

@@

\begin{question}
%[Related question] 
    If $\mu',\mu''$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
    \[
    \begin{tikzcd}
        \overline\Gr^{\lambda',\lambda'}_{0,s}\cap S^{\mu',\mu''}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda'} \cap S^{\mu'} \times \overline\Gr^{\lambda'} \cap S^{\mu''} \supset Z' \times Z'' \ar[d]\\
        \overline\OO^{\lambda',\lambda''}_{0,s} \cap \UU^{\mu',\mu''}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda'}\cap \TT_{\mu'}\cap \n \times \overline\OO^{\lambda''}\cap \TT_{\mu''}\cap \n
    \end{tikzcd}    
    \]
\end{question}
% 
\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z',Z''$  be MV cycles of coweight $(\lambda',\mu'),(\lambda'',\mu'')$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
    Then 
    \begin{equation}
        \label{eq:tabmult}
        % Z_\tau\ast Z_\sigma 
        m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
        = 
        % \sum_{Z\in\cZ(\lambda)_\mu} 
        \sum_{\tau\in S(\lambda)_\mu}
        i\left(
            X(\tau), X(\tau')\circ X(\tau'')
            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
        \right) [Z(\tau)]\,. 
    \end{equation}
    % and the intersection multiplicities on the right are found by\dots\acom{To be completed.}

@@

    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
    $$
    b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
        Z, Z' \circ Z''
        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
    \right) b_Z 
    $$
    can also be deduced from \Cref{eq:tabmult} for appropriate choices of $\lambda',\lambda''$ and $\mu',\mu''$. These are described in \Cref{lem:mintab,prop:minwts} below.
\end{proposition}
%

\acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
\begin{conjecture}
    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
    Let $\tau$ be the tableau of shape $\lambda$ and weight $\mu$ whose Lusztig datum is equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
    % Then $i(\tau, \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U})$ is equal to 1. 
    Then 
    \begin{equation}
        i(\tau, 
        % \pi^{-1}(0) \cdot \overline{\tau_1 \times \tau_2 \times U}
        % Z_1 \circ Z_2 
        \tau' \circ \tau''
        ) = 1 \,. 
    \end{equation}
\end{conjecture}
%

@@

We view MV cycles as semi-standard young tableaux. Suppose we have two tableaux $\tau'$ and $\tau''$, with respective weights $\lambda'$, $\mu'$ and $\lambda''$, $\mu''$, and we wished to take their fusion product. We consider a generic matrix $X \in \UU^{\mu',\mu''}_{0,s}$ and see what relations on the variables in $X$ occur when also asking for it to be in $\OO^{\lambda',\lambda''}_{0,s}$. \acom{Relations dictated by $\tau$. Can mostly refer the reader to the previous section for this background, now.}
